Glyph-maps for Visualizing Climate Data and Models

### 2011-09-28 paper.tex
Move acknowledgements to appropriate places in intro

  \item GISTEMP surface temperature data provided by the Earth System Research
  Laboratory, Physical Sciences Division, National Oceanic and Atmospheric
  Administration. This data is provided on $2^{\circ}$ x $2^{\circ}$ grid over
  the entire globe, continental United States (XXX locations), measured
  monthly. Ground station data was de-seasonalized, differenced from from the
  1951-1980 temperature averages, and spatially averaged to obtain gridded
  measurements. We extracted the locations corresponding to the continental
  USA.

  \item USHCN (Version 2) ground station network.

@@

All datasets and R code used to produce the plots are available in the online supplementary materials.

@@

\section*{Acknowledgements}

GISTEMP data provided by the NOAA/OAR/ESRL PSD, Boulder, Colorado,
USA, from their web site at \url{http://www.esrl.noaa.gov/psd/}.

USHCN data provided by NOAA NCDC from their website \url{http://cdiac.ornl.gov/ftp/ushcn_v2_monthly/}.

The graphics in this paper were created in R \citep{R} using {\tt ggplot2} \citep{me:ggplot2} and {\tt plyr} \citep{me:plyr}.

>>>>

  \item GISTEMP surface temperature data provided by the Earth System Research
  Laboratory, Physical Sciences Division, National Oceanic and Atmospheric
  Administration. This data is provided on $2^{\circ}$ x $2^{\circ}$ grid over
  the entire globe, continental United States (XXX locations), measured
  monthly. Ground station data was de-seasonalized, differenced from from the
  1951-1980 temperature averages, and spatially averaged to obtain gridded
  measurements. We extracted the locations corresponding to the continental
  USA. Provided by the NOAA/OAR/ESRL PSD, Boulder, Colorado,
  USA, from their web site at \url{http://www.esrl.noaa.gov/psd/}.

  \item USHCN (Version 2) ground station network. USHCN data provided by NOAA NCDC from their website \url{http://cdiac.ornl.gov/ftp/ushcn_v2_monthly/}.

@@

All datasets and R code used to produce the plots are available in the online supplementary materials. All plots were created in R \citep{R} using the {\tt ggplot2} \citep{me:ggplot2} and {\tt plyr} \citep{me:plyr} packages.

@@
